03 - Analyses coding

### 2022-06-28 scripts/r/03_analyses_coding.Rmd
♻️ - update analyses coding rmd

```{r forest-plot}
msa_models %>% 
  unnest(sum) %>% 
  mutate(
    typicality_lab = if_else(
      typicality == "cat", "Typicality = categorical", "Typicality = continuous"
    ), 
    mod_name = fct_reorder(mod_name, estimate)
  ) %>% 
  ggplot(aes(x = estimate, y = mod_name)) + 
  geom_vline(xintercept = 0) +
  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) +
  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") +
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```

>>>>

```{r forest-plot}
msa_models %>% 
  unnest(sum) %>%
  filter(mod_name != "polymetme_brevirostrum_1_dur_cat") %>%
  mutate(
    typicality_lab = if_else(
      typicality == "cat", "Typicality = categorical", "Typicality = continuous"
    ), 
    mod_name = fct_reorder(mod_name, estimate)
  ) %>% 
  ggplot(aes(x = estimate, y = mod_name)) + 
  geom_vline(xintercept = 0) +
  geom_segment(aes(x = estimate - se * 1.96, xend = estimate + se * 1.96, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) +
  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") +
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```
